APOGEE CATALOG OF 10,000+ M DWARFS MEASURED WITH DATA-DRIVEN MODELS

### 2018-07-30 paper/draft1/draft1.tex
update draft

APOGEE data products: ap1D, apVisit, apStar, and aspcapStar. We use the aspcapStar spectra, which contains the continuum-normalized, rest frame shifted, co-added spectrum of all observed epochs (see \citealt{Perez:2016} for a complete description of the pipeline). SNR of stars in our sample...

@@

Some note on what lines vary significantly with parameter...

@@

In \citealt{Schmidt:2016} the authors used three different color-temperature relations to check the consistency of ASPCAP temperature values.

>>>>

APOGEE data products: {\tt\string ap1D}, {\tt\string apVisit}, {\tt\string apStar}, and {\tt\string aspcapStar}. We use the {\tt\string aspcapStar} spectra, which contains the continuum-normalized, rest frame shifted, co-added spectrum of all observed epochs (see \citealt{Perez:2016} for a complete description of the pipeline). SNR of stars in our sample...

@@

\color{gcolor}{Some note on what lines vary significantly with parameter...}\color{black}

@@

In \citealt{Schmidt:2016} the authors used three different color-temperature relations to check the consistency of ASPCAP temperature values, using a combination of 2MASS and visual band photometries. \color{gcolor}{Brief description of the color-teff relations from \citealt{Casagrande:2008}, \citealt{Boyajian:2013}, and \citealt{Mann:2015}...}\color{black}.

To obtain visual band magnitudes for a set of sources, we cross-matched the 10,084 sources in our ``safe'' test sample to the AAVSO Photometric All-Sky Survey DR9 (APASS; \citealt{Henden:2016}), to obtain a subsample of 6,000 sources with both $BV$ photometries measured by APASS, and $JHK$ photometries from APOGEE. In Figure \ref{fig:aspcap_cannon_validation} we repeat the temperature validation tests for each of the three relations and compare the ASPCAP temperatures for the same sources. \color{gcolor}{Comments about validation results and the uncertainty of our Cannon temperatures...}\color{black}
